Figures

### 2019-05-02 figures/07_model-selection.Rmd
include dotplot in figures doc

# linear
model_form <- bf(tp ~ agvpct)
fit0 <- get_if_not_exists(brm_fit, "fit0.rds", formula = model_form, data = dt)
print("fixed effect")
print(fit0$formula)

# linear re
model_form <- bf(tp ~ (1 + agvpct | hu4vzoneid))
fit <- get_if_not_exists(brm_fit, "fit.rds", formula = model_form, data = dt)
# plot(fit)
# print(fit$formula)

# non-linear re
model_form <- bf(tp ~ bagvpct * agvpct, 
                 bagvpct ~ 1 + 
                   (1|hu4vzoneid), 
                 nl = TRUE)
fit1 <- get_if_not_exists(brm_fit, "fit1.rds", formula = model_form, data = dt)
# plot(fit1)
print("random effects")
print(fit1$formula)

# non-linear re w/ 2nd level coeffs
model_form2 <- bf(tp ~ bagvpct * agvpct, 
                 bagvpct ~ 1 + phosphorusvfertilizervuse + soybeans +
                   (1|hu4vzoneid), 
                 nl = TRUE)
fit2 <- get_if_not_exists(brm_fit, "fit2.rds", formula = model_form2, data = dt)
print("re w/ 2nd level coeffs")
print(fit2$formula)

>>>>

# linear
model_form <- bf(tp ~ agvpct)
fit0 <- get_if_not_exists(brm_fit, "../data/mcmc/fit0.rds", formula = model_form, 
                          data = dt)
print("fixed effect")
print(fit0$formula)

# linear re
model_form <- bf(tp ~ (1 + agvpct | hu4vzoneid))
fit <- get_if_not_exists(brm_fit, "../data/mcmc/fit.rds", formula = model_form, 
                         data = dt)
# plot(fit)
# print(fit$formula)

# non-linear re
model_form <- bf(tp ~ bagvpct * agvpct, 
                 bagvpct ~ 1 + 
                   (1|hu4vzoneid), 
                 nl = TRUE)
fit1 <- get_if_not_exists(brm_fit, "../data/mcmc/fit1.rds", formula = model_form, 
                          data = dt)
# plot(fit1)
print("random effects")
print(fit1$formula)

# non-linear re w/ 2nd level coeffs
model_form2 <- bf(tp ~ bagvpct * agvpct, 
                 bagvpct ~ 1 + phosphorusvfertilizervuse + soybeans +
                   (1|hu4vzoneid), 
                 nl = TRUE)
fit2 <- get_if_not_exists(brm_fit, "../data/mcmc/fit2.rds", formula = model_form2, 
                          data = dt)
print("re w/ 2nd level coeffs")
print(fit2$formula)

### 2019-05-02 figures/08_exploratory_dotplot.Rmd
include dotplot in figures doc

# pheatmap::pheatmap(
#   t(dt_tp),  
#   color = colorRampPalette(RColorBrewer::brewer.pal(n = 7, name =
#                                             "Reds"))(100),
#   cluster_cols = FALSE, cluster_rows = FALSE, 
#   na.col = "grey", 
#   cellheight = 7)
# 
# pheatmap::pheatmap(
#   t(dt_tn),  
#   color = colorRampPalette(RColorBrewer::brewer.pal(n = 7, name =
#                                                       "Reds"))(100),
#   cluster_cols = FALSE, cluster_rows = FALSE, 
#   na.col = "grey", 
#   cellheight = 7)

>>>>

# ----
dt_tp_hmap <- dt_sub %>%
  corrr::correlate() %>%
  # corrr::shave() %>%
  # janitor::remove_empty(c("rows", "cols")) %>%
  mutate_if(is.numeric, round, 2) %>%
  data.frame()

dt_tp_rows       <- dt_tp_hmap$rowname
dt_tp_hmap            <- dt_tp_hmap %>%
  dplyr::select(-rowname) %>%
  mutate_all(abs)
row.names(dt_tp_hmap) <- dt_tp_rows

pheatmap::pheatmap(
  t(dt_tp_hmap),
  color = colorRampPalette(RColorBrewer::brewer.pal(n = 7, name =
                                            "Reds"))(100),
  cluster_cols = TRUE, cluster_rows = TRUE,
  na.col = "grey",
  cellheight = 7)
# 
# pheatmap::pheatmap(
#   t(dt_tn),  
#   color = colorRampPalette(RColorBrewer::brewer.pal(n = 7, name =
#                                                       "Reds"))(100),
#   cluster_cols = FALSE, cluster_rows = FALSE, 
#   na.col = "grey", 
#   cellheight = 7)

### 2019-05-02 manuscript/figures.Rmd
stash completed dotplot, closes #8
include dotplot in figures doc

>>>>

```{r exploratory_heatmap, fig.cap = "Exploratory heatmap showing absolute value correlations.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/08_exploratory_dotplot-1.pdf")
```

```{r exploratory_dotplot, fig.cap = "Exploratory dotplots showing absolute value correlations.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/08_exploratory_dotplot-2.pdf")
```
